Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-18 content/example.tex
remove line numbers from short code snippets

\subsection{An Example from the Scala Collections Library}
The Scala collections library contains the trait \code{TraversableOnce} that is
shared by both collections and iterators over them. 
\ftodo{
  I think it would be helpful to show a little more of the code of the trait here,
  such as the trait declaration and the signature of the toArray method containing the
  correlated calls. You can abbreviate everything else with ...
}
The \code{toArray} method of this trait
creates an array and copies the contents of the collection or iterator into it:
\inputMinted{scala}{collectionsExample.scala}
%\otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
When \code{this} refers to an iterator rather than a collection, the call to \code{this.size}
extracts all elements of the iterator to count them.
\ftodo{
  Would it make sense to show the code for the size method, and refer to the line numbers
  of that method in the above sentence?  
}
 At the call to \code{copyToArray},
the iterator is already empty, so nothing is copied to the newly created array.
\ftodo{
Would it make sense to show the code for copyToArray here?
}
One could design an IFDS analysis to detect this kind of bug.

However, the implementation of \code{TraversableOnce.toArray} is actually correct because the above
code is guarded with a test:
\inputMinted{scala}{isTraversable.scala}
\ftodo{
  It is confusing that this code fragment is labeled with line number 19 although it presumably
  occurs in the code before the previously discussed two lines. I think it is better to show
  all of the code at once, in a figure, and include at least the headers of all the methods mentioned
  here.
}
When the \code{isTraversableAgain} method returns false, as it does for
an iterator, the \code{toArray} method uses a different
(less efficient) implementation. The bug report would therefore be a false positive. 
The \code{isTraversableAgain} method is easy to analyze: it returns the constant
true in a collection and the constant false in an iterator. However, in order
to eliminate the false positive bug report, an analysis would need to rule out infeasible
paths using correlated calls. Specifically, the following path triggers the bug, but
is infeasible: first, call \code{isTraversableAgain} on a collection, returning
true, then call \code{size} and \code{copyToArray} on an iterator. Our correlated
calls analysis could determine that this path is infeasible because it calls the
collection version of \code{isTraversableAgain} but the iterator versions of
\code{size} and \code{copyToArray}.
\ftodo{Would it be helpful to create a diagram of the relevant fragments of the supergraph,
with the infeasible path in bold?}

>>>>

\subsection{An Example from the Scala Collections Library}
The Scala collections library contains the trait \code{TraversableOnce} that is
shared by both collections and iterators over them. 
\ftodo{
  I think it would be helpful to show a little more of the code of the trait here,
  such as the trait declaration and the signature of the toArray method containing the
  correlated calls. You can abbreviate everything else with ...
}
The \code{toArray} method of this trait
creates an array and copies the contents of the collection or iterator into it:
\inputMintedNoLNs{scala}{collectionsExample.scala}
%\otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
When \code{this} refers to an iterator rather than a collection, the call to \code{this.size}
extracts all elements of the iterator to count them.
\ftodo{
  Would it make sense to show the code for the size method, and refer to the line numbers
  of that method in the above sentence?  
}
 At the call to \code{copyToArray},
the iterator is already empty, so nothing is copied to the newly created array.
\ftodo{
Would it make sense to show the code for copyToArray here?
}
One could design an IFDS analysis to detect this kind of bug.

However, the implementation of \code{TraversableOnce.toArray} is actually correct because the above
code is guarded with a test:
\inputMintedNoLNs{scala}{isTraversable.scala}
\commentout{
\ftodo{
  It is confusing that this code fragment is labeled with line number 19 although it presumably
  occurs in the code before the previously discussed two lines. I think it is better to show
  all of the code at once, in a figure, and include at least the headers of all the methods mentioned
  here.
}
}
When the \code{isTraversableAgain} method returns false, as it does for
an iterator, the \code{toArray} method uses a different
(less efficient) implementation. The bug report would therefore be a false positive. 
The \code{isTraversableAgain} method is easy to analyze: it returns the constant
true in a collection and the constant false in an iterator. However, in order
to eliminate the false positive bug report, an analysis would need to rule out infeasible
paths using correlated calls. Specifically, the following path triggers the bug, but
is infeasible: first, call \code{isTraversableAgain} on a collection, returning
true, then call \code{size} and \code{copyToArray} on an iterator. Our correlated
calls analysis could determine that this path is infeasible because it calls the
collection version of \code{isTraversableAgain} but the iterator versions of
\code{size} and \code{copyToArray}.
\ftodo{Would it be helpful to create a diagram of the relevant fragments of the supergraph,
with the infeasible path in bold?}
